Lesson 4
========================================================

***

### Diamonds dataset

####Quiz 1: Load dataset
a) How many observations are in data set?:
```{r}
library(ggplot2)

dim(diamonds)[1]
```

b) How many variables are in dataset?
```{r}
dim(diamonds)[2]
```
c) How many ordered factors?
```{r}
str(diamonds)
```
**Answer:** 3

d) What letters represent the best color for a diamond?
**Answer:** "D"

####Quiz 2:Create a histogram of the price of all the diamonds in the diamond data set

```{r}
ggplot(diamonds, aes(x = price)) +
  geom_histogram(binwidth = 400, color = "white", fill = "blue") +
  geom_freqpoly()
```
####Quiz 3 Describe shape and price distribution. Include sammary statistics
The distribution is right skwed.
```{r}
summary(diamonds$price)
```

#### Quiz 4 - Diamond Counts
a) How many diamonds cost less than $500?
```{r}
summary(diamonds$price < 500)
```
b) How many diamonds cost less than $250?
```{r}
summary(diamonds$price < 250)
```
c) How many diamonds cost $15,000 or more?
```{r}
summary(diamonds$price >= 15000)
```

#### Quiz 5 - Cheaper diamonds
Explore the largest peak in the price histogram you created earlier.
Try limiting the x-axis, altering the bin width, and setting different breaks on the x-axis.
There won’t be a solution video for this question so go to the discussions to share your thoughts and discover what other people find.

You can save images by using the ggsave() command. ggsave() will save the last plot created.
For example...
                  qplot(x = price, data = diamonds)
                  ggsave('priceHistogram.png')

ggsave currently recognises the extensions eps/ps, tex (pictex),
pdf, jpeg, tiff, png, bmp, svg and wmf (windows only).

```{r}
ggplot(diamonds, aes(x = price)) +
  geom_histogram(binwidth = 50, color = "white", fill = "blue") +
  geom_freqpoly(binwidth = 50) +
  scale_x_continuous(limits = c(300, 2000))
```

#### Quiz 6 - Price by Cut Historgam  
Break out the histogram of diamond prices by cut.
You should have five histograms in separate panels on your resulting plot.

```{r}
ggplot(diamonds, aes(x = price)) +
  geom_histogram(binwidth = 500, color = "white", fill = "blue") +
  facet_wrap(~cut, scales = "free_y", ncol = 2)
  #scale_x_continuous(limits = c(300, 2000))
```
```{r}
by(diamonds$price, diamonds$cut, summary)
```
#### Quiz 7 - Price by Cut  
Answer the question below. Check more than one opton if there are ties   
* **a)** Which cut has the highest priced diamond?
**Answer:** Premium - 18823
```{r}
sort(by(diamonds$price, diamonds$cut, max))
```
* **b)** Which cut has the lowest priced diamond?
```{r}
sort(by(diamonds$price, diamonds$cut, min))
```
* **c)** Which cut has the lowest median price?
```{r}
sort(by(diamonds$price, diamonds$cut, median))
```

### Quiz 9: Price per Carat by Cat
Create a histogram of price per carat and facet it by cut. You can make adjustments
to the code from the previous exercise to get started.
Adjust the bin width and transform the scale of the x-axis using log10.

```{r}
ggplot(diamonds, aes(x = price / carat)) +
  geom_histogram(bins = 50, color = "white", fill = "blue") +
  scale_x_log10() +
  facet_wrap(~cut, scales = "free_y", ncol = 2)
```
### Quiz 10: Price Box Plot
Investigate the price of diamonds using box plots, numerical summaries, and one of the following categorical
variables: cut, clarity, or color. 
```{r}
ggplot(diamonds, aes(y = price / carat, x = cut)) +
  geom_boxplot() +
  coord_cartesian(ylim = c(300, 1e4))
```
Summary statistics:
```{r}
by(diamonds$price / diamonds$carat, diamonds$cut, summary)
```
### Quiz 11: Interquartile Range
```{r}
fife_stat <- by(diamonds$price, diamonds$color, summary)
```
* **a)** What is the price range for the middle 50% of diamonds of color D?
```{r}
fife_stat$D
```

* **b)** What is the price range for the middle 50% of diamonds of color J?
```{r}
fife_stat$J
```

* **c)** What is the IQR for diamonds with the best color?
```{r}
IQR_color <- by(diamonds$price, diamonds$color, IQR)
IQR_color["D"]
```

* **d)** What is the IQR for diamonds with the best color?
```{r}
IQR_color["J"]
```

### Quiz 12: Price per Carat Box Plots by Color  
Investigate the price per carat of diamonds across the different colors of diamonds using boxplots.

```{r}
ggplot(diamonds, aes(x = color, y = price / carat)) +
  geom_boxplot() +
  coord_cartesian(ylim = c(900, 8e3))
```

### Quiz 13 - Carat Frequency Polygon
Investigate the weight of the diamonds (carat) using a frequency poligon.
binwidth = range / bin
```{r}
ggplot(diamonds, aes(x = carat)) +
  geom_freqpoly(binwidth = 0.05)
```

What carat size has a count greater than 2000?
```{r}
ggplot(diamonds, aes(x = carat)) +
  geom_freqpoly(binwidth = .001) +
  coord_cartesian(xlim = c(0, 2))
```

**Answer:** 0.3 and 1.1 carat

###Quiz 16 - Exploring Your Friends' Birthdays
Your task is to investigate the distribution of your friends' birth months and days.

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

