Lesson 3
========================================================

```{r setup, include = FALSE}
knitr::opts_chunk$set(
    fig.width = 9,
    fig.height = 7)
```

***

### What to Do First?
Notes:

***

### Pseudo-Facebook User Data
Notes:

```{r Pseudo-Facebook User Data}
pf <- read.csv("eda-course-materials/lesson3/pseudo_facebook.tsv", sep = '\t')
```

***

### Histogram of Users' Birthdays
Notes:

```{r Histogram of Users\' Birthdays}
library(ggplot2)
library(ggthemes)

ggplot(aes(x = dob_day), data = pf) +
    geom_histogram(binwidth = 1, color = "white", fill = "black") +
    scale_x_continuous(breaks = 1:31, expand = c(0, 0))
```

***

#### What are some things that you notice about this histogram?
Response:

***

### Moira's Investigation
Notes:

***

### Estimating Your Audience Size
Notes:

***

#### Think about a time when you posted a specific message or shared a photo on Facebook. What was it?
Response:

#### How many of your friends do you think saw that post?
Response:

#### Think about what percent of your friends on Facebook see any posts or comments that you make in a month. What percent do you think that is?
Response:

***

### Perceived Audience Size
Notes:

***
### Faceting
Notes:

```{r Faceting}
ggplot(aes(x = dob_day), data = pf) +
    geom_histogram(binwidth = 1, color = "white", fill = "black") + 
    scale_x_continuous(breaks = 1:31) + 
    facet_wrap(~dob_month)
```

#### What code would you enter to create a histogram of friend counts?

```{r Friend Count}
ggplot(aes(x = friend_count), data = pf) +
    # geom_histogram() +
    geom_histogram(binwidth = 100, color = "white", fill = "black") +
    scale_y_log10(expand = c(0, 0), breaks = c(0, 1e1, 1e2, 1e3, 5e3, 1e4, 3e4)) +
    scale_x_continuous(limits = c(-1, 5000), expand = c(0.02, 0))
```

#### How is this plot similar to Moira's first plot?
Response:

```{r}
ggplot(aes(x = friend_count), data = pf) +
    geom_histogram()
#qplot(x = friend_count, data = pf)
```



### Exploring with Bin Width
Notes:

***

### Adjusting the Bin Width
Notes:

### Faceting Friend Count
```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.

ggplot(aes(x = friend_count), data = pf) +
  geom_histogram(binwidth = 100, color = "white", fill = "black") +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) +
  facet_wrap(~gender)
```

***

### Omitting NA Values
Notes:

```{r Omitting NA Values}
ggplot(aes(x = friend_count), data = subset(pf, !is.na(gender))) +
  geom_histogram(binwidth = 30, color = "white", fill = "black") +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) +
  facet_wrap(~gender)
```

***

### Statistics 'by' Gender
Notes:

```{r Statistics \'by\' Gender}
gender_sum <- by(pf$friend_count, pf$gender, summary)
gender_sum
```

#### Who on average has more friends: men or women?
Response:
Women
#### What's the difference between the median friend count for women and men?
Response:
`r gender_sum$female[["Median"]] - gender_sum$male[["Median"]]`
#### Why would the median be a better measure than the mean?
Response:

***

### Tenure
Notes:

```{r Tenure}
ggplot(aes(x = tenure), data = pf) + 
    geom_histogram(binwidth = 30, color = 'black', fill = '#099DD9')
```

***

#### How would you create a histogram of tenure by year?

```{r Tenure Histogram by Year}
ggplot(aes(x = tenure / 365), data = pf) + 
    geom_histogram(binwidth = .1, color = 'black', fill = '#099DD9') +
    scale_x_continuous(breaks = seq(1, 7, 1), limits = c(0,7))
```

***

### Labeling Plots
Notes:

```{r Labeling Plots}
ggplot(aes(x = tenure / 365), data = pf) +
    xlab("Number of years using Facebook") +
    ylab("Number of users in sample") +
    geom_histogram(binwidth = .25, color = 'black', fill = '#099DD9') +
    scale_x_continuous(breaks = seq(1, 7, 1), limits = c(0,7))
```

***

### User Ages
Notes:

```{r User Ages}
ggplot(aes(x = age), data = pf) +
    xlab("Age of users in sample") +
    ylab("Number of users using Facebook") +
    geom_histogram(binwidth = 1, color = 'black', fill = '#099DD9') +
    scale_y_continuous(expand = c(0, 0)) +
    scale_x_continuous(breaks = seq(10, 120, 10), limits = c(10,120), expand = c(0, 0)) +
    theme_classic()
```
```{r}
ggplot(aes(x = age), data = pf) +
    xlab("Age of users in sample") +
    ylab("Number of users using Facebook") +
    geom_histogram(binwidth = 2, color = 'black', fill = '#099DD9') +
    scale_x_continuous(breaks = seq(10, 120, 10), limits = c(10,120)) +
    theme_classic() +
    theme(axis.line = element_blank())
```

### Transforming Data
Notes:

***

### Add a Scaling Layer
Native scale:
```{r Add a Scaling Layer}
summary(pf$friend_count)

p1 <- ggplot(aes(x = friend_count), data = pf) +
    geom_histogram(color = 'black', fill = '#099DD9')
p1
```
Log10 scale:
```{r}
summary(log10(pf$friend_count + 1))

p2 <- ggplot(aes(x = friend_count), data = pf) +
    geom_histogram(binwidth = .1, color = 'black', fill = '#099DD9') +
    scale_x_log10()
p2
```
Sqrt scale:
```{r}
summary(sqrt(pf$friend_count))

p3 <- ggplot(aes(x = friend_count), data = pf) +
    geom_histogram(binwidth = 1, color = 'black', fill = '#099DD9') +
    scale_x_sqrt(breaks = c(0, 100, 500, 1000, 2000, 5000))
p3
```
Multiple charts:
```{r}
library("gridExtra")
grid.arrange(p1, p2, p3)
```


***


### Frequency Polygons

```{r Frequency Polygons}
ggplot(aes(x = friend_count, y = ..count.. / sum(..count..)),
       data = subset(pf, !is.na(gender))) +
    geom_freqpoly(aes(color = gender), binwidth = 10) +
    scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) +
    xlab("Friend count") +
    ylab("Proportion of users with that friend count") +
    theme_classic()
```
My notes:
```{r}
bp0 <- ggplot(aes(x = friend_count, y = ..count.. / sum(..count..)),
       data = subset(pf, !is.na(gender))) +
    geom_freqpoly(aes(color = gender), binwidth = 10) +
    xlab("Friend count") +
    ylab("Proportion of users with that friend count")

bp1 <- bp0 + scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50))
bp2 <- bp0 + scale_x_continuous(limits = c(300, 600), breaks = seq(0, 1000, 50))
grid.arrange(bp1, bp2, ncol = 1)
```


***

### Likes on the Web
Notes:

```{r Likes on the Web}
ggplot(aes(x = www_likes), data = subset(pf, !is.na(gender))) +
    geom_freqpoly(aes(color = gender), binwidth = .1) +
    scale_x_log10()
```

```{r}
by(pf$www_likes, pf$gender, sum)
```

***

### Box Plots
Notes:

```{r Box Plots}
ggplot(data = subset(pf, !is.na(gender)), aes(x = gender, y = friend_count)) +
  geom_boxplot()
```

#### Adjust the code to focus on users who have friend counts between 0 and 1000.

```{r}
ggplot(data = subset(pf, !is.na(gender)), aes(x = gender, y = friend_count)) +
  geom_boxplot() +
  scale_y_continuous(limits = c(0, 250))
```

***

#### Let's see the same information with **summary** function:

```{r}
friends <- by(pf$friend_count, pf$gender, summary)
friends
```

#### Important part!
On ghaph above we see that using scale_y_continuous(limits = c(0, 250) dropped out 19870 points from dataset to build the chart. So the boxplot does not represent correct picture. Let`s use coord_cortesian instead: 

```{r}
ggplot(data = subset(pf, !is.na(gender)), aes(x = gender, y = friend_count)) +
  geom_boxplot() +
  coord_cartesian(ylim = c(0, 500))
```


### Box Plots, Quartiles, and Friendships
Notes:

```{r Box Plots, Quartiles, and Friendships}
ggplot(data = subset(pf, !is.na(gender)), aes(x = gender, y = friendships_initiated)) +
  geom_boxplot() +
  coord_cartesian(ylim = c(0, 150))
```

#### On average, who initiated more friendships in our sample: men or women?
Response: women
#### Write about some ways that you can verify your answer.
Response:
```{r Friend Requests by Gender}
by(pf$friendships_initiated, pf$gender, summary)
```

***

### Getting Logical
Notes:

```{r Getting Logical}
pf$mobile_check_in <- ifelse(pf$mobile_likes > 0, 1, 0)
pf$mobile_check_in <- factor(pf$mobile_check_in)
summary(pf$mobile_check_in)
```
#### What percent of check in using mobile?
```{r}
mb <- summary(pf$mobile_check_in)
mb[[2]] / (mb[[1]] + mb[[2]])
sum(pf$mobile_likes_received == 1)/length(pf$mobile_check_in) 
```

Response: 64.59%

***

### Analyzing One Variable
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!