Lesson 4-5
========================================================

```{r setup, include = FALSE}
knitr::opts_chunk$set(
    fig.width = 9,
    fig.height = 7)
```

***

### Scatterplots and Perceived Audience Size
```{r}
library(ggplot2)
pf <- read.csv("eda-course-materials/lesson3/pseudo_facebook.tsv", sep = '\t')
```

***

### Scatterplots

```{r Scatterplots}
ggplot(pf, aes(x = age, y = friend_count)) +
  geom_point()
```

***
#### Correct age scale
```{r}
summary(pf$age)
```
```{r}
ggplot(pf, aes(x = age, y = friend_count)) +
  geom_point() +
  xlim(13, 90)
```


### Overplotting
Notes:

```{r Overplotting}
ggplot(pf, aes(x = age, y = friend_count)) +
  geom_jitter(alpha = 1/20) +
  xlim(13, 90)
```

### Coord_trans()

```{r Coord_trans}
ggplot(pf, aes(x = age, y = friend_count)) +
  geom_point(alpha = 1/20, position = position_jitter(h = 0)) +
  xlim(13, 90) +
  coord_trans(y = "sqrt", limy = c(1, 4923))
```

### Quiz 7

```{r Coord_trans}
ggplot(pf, aes(x = age, y = friendships_initiated)) +
  geom_point(alpha = 1/20, position = position_jitter(h = 0)) +
  xlim(13, 90) +
  coord_trans(y = "sqrt", limy = c(1, 2000))
```

### Conditional Means
Notes:

```{r Conditional Means}
library(dplyr)
library(magrittr)

pf.fc_by_age <- pf %>% 
  group_by(age) %>% 
  summarise(friend_count_mean = mean(friend_count),
            friend_count_median = median(friend_count),
            n = n()) %>% 
  arrange(age)
```

Plot mean friend count vs. age using a line graph. Be sure you use the correct variable names and the correct data frame. You should be working with the new data frame created from the dplyr functions. The data frame is called 'pf.fc_by_age'. Use geom_line() rather than geom_point to create the plot. You can look up the documentation for geom_line() to see what it does.
   
Create your plot!

```{r Conditional Means Plot}
ggplot(pf.fc_by_age, aes(y = friend_count_mean, x = age)) +
  geom_line()
```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}
ggplot(pf, aes(x = age, y = friendships_initiated)) +
  geom_point(alpha = 1/20,
             position = position_jitter(h = 0),
             color = "orange") +
  coord_cartesian(xlim = c(13, 90), ylim = c(1, 1000)) +
  coord_trans(y = "sqrt", limy = c(1, 1000), limx = c(13, 90)) +
  geom_line(stat = "summary", fun.y = mean) +
  geom_quantile(quantiles = c(.1, .5, .9), method = "rqss", lambda = 0.1,
                color = "blue", linetype = 2) 
```

#### What are some of your observations of the plot?
Response:

***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}

```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(                 , cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:

***

## Create Scatterplots
Notes:

```{r}

```

***

### Strong Correlations
Notes:

```{r Strong Correlations}

```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}

```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)
```

Create your plot!

```{r Temp vs Month}

```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}

```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}

```

***

### A New Perspective

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}

```

***

### Age with Months Means

```{r Age with Months Means}

```

Programming Assignment
```{r Programming Assignment}

```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}

```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}

```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

